Large-scale text pre-training helps with dialogue act recognition, but not without fine-tuning

### 2021-03-12 reports/IWCS2021/iwcs-short-paper.tex
typo

There is some previous work applying BERT to dialogue.
\citet{baoPLATOPretrainedDialogue2019} and \citet{chenSemanticallyConditionedDialog2019a} both use BERT for dialogue generation tasks.
Similarly, \citet{vigComparisonTransferLearningApproaches2019} find BERT useful for selecting a response from a list of candidate responses in a dialogue.
\citet{mehriPretrainingMethodsDialog2019} evaluate BERT in various dialogue tasks including DAR, and find that a model incorporating BERT outperforms a baseline model.
Finally, \citet{chakravarty2019dialog} use BERT for dialogue act classification for a proprietary domain and achieves promising results, and \citet{ribeiro2019deep} surpass the previous state-of-the-art on generic dialog act recognition for Switchboard and MRDA corpora. 
This paper aims to supplement the findings of previous work by investigating how much of 
BERT's sucess for dialogue tasks is due to its extensive pre-training and how much is due to 
task-specific fine-tuning.

>>>>

There is some previous work applying BERT to dialogue.
\citet{baoPLATOPretrainedDialogue2019} and \citet{chenSemanticallyConditionedDialog2019a} both use BERT for dialogue generation tasks.
Similarly, \citet{vigComparisonTransferLearningApproaches2019} find BERT useful for selecting a response from a list of candidate responses in a dialogue.
\citet{mehriPretrainingMethodsDialog2019} evaluate BERT in various dialogue tasks including DAR, and find that a model incorporating BERT outperforms a baseline model.
Finally, \citet{chakravarty2019dialog} use BERT for dialogue act classification for a proprietary domain and achieves promising results, and \citet{ribeiro2019deep} surpass the previous state-of-the-art on generic dialogue act recognition for Switchboard and MRDA corpora. 
This paper aims to supplement the findings of previous work by investigating how much of 
BERT's sucess for dialogue tasks is due to its extensive pre-training and how much is due to 
task-specific fine-tuning.
